Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2010-04-30 paper/graph.tex
minor fix
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@598 3fc257bb-8550-0410-81b3-a5c103da83f7

As with PageRank and R-MAT generation, 
significant savings in communication and execution time
can be achieved by pre-aggregating certain MapReduce objects and 
storing data in more than one MapReduce object.  The improved algorithm
is shown in Figure~\ref{fig:sssp2}.  The MapReduce objects storing
vertices and edges are aggregated to processors only once at the beginning
of the computation.  Then, in each iteration of 
SSSP, only a small number of new candidate distances are generated.
The improved algorithm uses MapReduce object $MR$ to store these updates.
All communication is performed using $MR$, so the total amount of communication
needed is small compared to the original algorithm (which aggregates all
graph edges in each iteration).  Updated vertex distances are stored back
in the the MapReduce object for vertices.

>>>>

As with PageRank and R-MAT generation, 
significant savings in communication and execution time
can be achieved by pre-aggregating certain MapReduce objects and 
storing data in more than one MapReduce object.  The improved algorithm
is shown in Figure~\ref{fig:sssp2}.  The MapReduce objects storing
vertices and edges are aggregated to processors only once at the beginning
of the computation.  Then, in each iteration of 
SSSP, only a small number of new candidate distances are generated.
The improved algorithm uses MapReduce object $U$ to store these updates.
Only the updates are communicated; each update is aggregated to the 
same processor that stores the corresponding vertex and its edges.
Communication is performed using $U$, so the total amount of communication
needed is small compared to the original algorithm (which aggregates all
graph edges in each iteration).  Updated vertex distances are stored back
in the the MapReduce object for vertices.
